Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-03-05 ongoing/report/3_theorems_and_proofs.tex
Reformatting source

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \m{g \in \MB{C}^{N_g}}, and we continue to use \m{\hat{g}} to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \m{\V{P}}, \m{\V{g}}, \m{\V{y}}, and \m{\V{z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \m{\RM{supp}(\V{g})} has roughly cardinal \m{L}, which guarantees, at the heart of the argument, that \m{\V{g}} is almost-sparse

@@

We apply DS to find \m{\hat{\V{g}}}, setting
\Disp{
\NC \gamma = \NC \R{2 \log N_g} \NR[+]
}

Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
\NC \V{d} = \NC \hat{\V{g}} -\V{g} \NR[+]
}
%
And call
\startitemize
\item \m{\MC{A}} be the largest \m{s} position of \m{g}.
\item \m{\MC{B}} be the largest \m{s} position of \m{d_{T(N_g) -\MC{A}}}.
\item \m{\MC{C} =T \RB{ N_g } -\MC{A}}, i.e., the complementary index set of \m{\MC{A}}.
\stopitemize

Suppose \m{\M{A} \in \MB{M}_{\MB{K}} \RB{ N_1, N_2 }}.
For brevity, let \m{\MC{T} \subset T \RB{ N_2 }}.
Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
Let \m{S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)}, \m{N \in \MB{N}}, be the sorting function for \m{x \in \MB{V}_{\MB{K}}(N))}, so that
\Disp{
\NC \Nm{S \RB{x} \DB{n_1}} \geq  \NC \Nm {S \RB{x} \DB{n_2}}, \NR[+]
\NC n_1 > \NC n_2,
\quad n_1, n_2 \in T\RB{N} \NR
}
Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m{S} throughout this article.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.

\Result
{Definition}
{
Let function \m{f:\; T\RB{N} \mapsto \MB{R}_+}, \m{N \in \MB{N}}, be given.
For \m{x \in \MB{V}_{\MB{K}}(N)}, we say \m{x} is confined in sorted magnitude according to \m{f}, if
\Disp{
\NC \Nm {S(x) \DB{ n } } < \NC f (n),
\quad n \in T\RB{N}. \NR
}
}

\Result
{Definition}
{
For \m{\V{x} \in \MB{V}_{\MB{K}}(N)}, we say \m{\V{x}} is almost-\m{s}-sparse with \m{\ell_1}-residue \m{R}, if
\Disp{
\NC \sum_{n=s+1}^N \Nm {S(\V{x}) (n)}
\leq \NC R. \NR
}
}

\Result
{Lemma (Tentative)}
{
Suppose \m{0 \leq \f \leq 2\pi k /N_H}, \m{k =0, \dots, N_H-1}.
Let \m{\f} be given, and array response \m{\V{a} (\f)} defined as in ().
Then \m{\V{a} (\f)} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
%
\Disp{
\NC R
\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
}
}

We show the lemma, which is the key to bounding the sparsity of \m{h}.
Recall the identity for Dirichlet kernel
%
\Disp{
\NC D (\f')
:= \NC \Nm{ \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} } \NR
\NC = \NC \F{\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\NC \sin x = \NC x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1 \NR
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\NC \Nm{x - \F{x^3}{6}} \leq \NC \Nm{\sin x}, \NR[+]
\NC -\pi \leq \NC x \leq \pi \NR
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\NC \Nm{ D (\f') }
= \NC \F{48}{\Nm {\f'^2 -24} \Nm {\f'}}
\quad 0 \leq \f' \leq \pi. \NR
}

Particularly, for arbitrary \m{\f}, find \m{k} so that
\Disp{
\NC \eta := \NC \f -\F{2\pi k}{N_H}, \NR[+]
\NC \Nm {\eta}
\leq \NC \F{2\pi}{N_H}. \NR
}
%
Then observe
\Disp{
\NC \RB {\M{K}^\H \V{a}(\f)} \DB {k}
=\NC \F{1}{N_H} D \RB{\f -\F{2 \pi k} {N_H}} \NR
}
So we need only bound
\Disp{
\NC R(\eta)
:=\NC \F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB{ \eta +\F{2 \pi n_H} {N_H} } \NR
}
By the approximation of rectangle to integral,
\Disp{
\NC R(\eta) -\F{2\pi} {N_H}
\leq \NC \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
}
Bound \m{D} by above technique, meanwhile we notice \m{\f' <24}.
\Disp{
\NC R(\f)
\leq \NC \F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NR
\NC = \NC \F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \m{<1}, and we drop that.
Also drop \m{2\pi /N_H} since it is small.
Furthermore the \m{2\pi} factor in log can be dropped too.
\Disp{
\NC R(\f)
\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
}

\Result
{Lemma (Tentative)}
{
Let \m{\f} and \m{\th} be uniformly, independently distributed in \m{[0,2\pi)}, and linear array response \m{\V{a}} defined as in ().
Let \m{\V{g}} be defined as above.
Then \m{\V{g}} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
%
\Disp{
\NC R
\leq \NC \F{L}{\pi^2} \RB{ \log \F{N_H}{L} }^2 \NR
}
}

@@

\Result
{Definition}
{
For \m{\MC{T}, \MC{T}' \subset \{1, \dots, N_p\}}, define the \m{s, s'}-restricted orthogonality constant \m{\tau_{s,s'} >0} to be the smallest such that
%
\Disp{
\NC \Nm {\IP {P_{\MC{T}} h, P_{\MC{T}'} h'}}
\leq \NC \tau_{s, s'} \cdot \VNm { h } _2 \VNm {h'} _2 \NR
}
}

@@

\Result
{Lemma}
{
Let \m{P} be given.
Then \m{\tau_{s, s'}} is bounded in both direction as follows,
\Disp{
\NC \d_{s+s'} -\max (\{\d_s, \d_{s'}\})
\leq \NC \tau_{s, s'} \NR
\NC \leq \NC \d_{s+s'}
}
}

Thus \m{\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \m{\d_s} only.

\Result
{Lemma}
{
Let \m{P} be i.i.d.\ Radmacher, as defined in Lemma ().
Then \m{P} is RIP according to \m{\d} for at least probability
\Disp{
\NC 1 -2 \RB{ \F{12}{\d} }^s \exp \left[ - \RB{ \F{\epsilon^2}{4} -\F{\epsilon^3}{6} } \F{\d}{2} N_p \right] \NR
}
}

@@

\Result
{Proposition}
{
Let \m{\V{g}} and \m{\V{d}} be defined as above.
Then
%
\Disp{
\NC \VNm {\V{d}_{\MC{C}}} _1
\leq \NC \VNm {\V{d}_{\MC{A}}} _1 +2\VNm {\V{g}_{C}} _1 \NR
}
}

To show this, observe that with triangle inequality applied respectively on \m{\MC{A}} and \m{\MC{C}},
\Disp{
\NC \VNm {\V{g}} _1
-\VNm {\V{d}_{\MC{A}}} _1
+\VNm {\V{d}_{\MC{C}}} _1
-\VNm {\V{g}_{\MC{C}}} _1
\leq \NC \VNm {\V{g} +\V{d}} _1 \NR
}
In the first line, we recall \m{\V{g} =\V{g}_{\MC{A}}}.
On the other hand, by construction that \m{\hat{g}} minimizes the \m{\ell_1}-norm,
\Disp{
\NC \VNm {\V{g} +\V{d}} _1
=\NC \VNm {\hat{\V{g}}} _1 \NR
\NC \leq \NC \VNm {\V{g}} _1 \NR
}
The result follows by combining.

\Result
{Lemma}
{
Let \m{\V{z}} and \m{\M{P}} be defined as above.
Then
%
\Disp{
\NC \Nm {\IP{ \V{z}, \M{P}(:, n_g) }}
\leq \NC  2 \R{\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
%
with overwhelming probability.
}

This only depends on the fact that \m{\M{P}(:, n_g)} has unity \m{\ell_2}-norm, and on the randomness of \m{\V{z}}.

Recall the following bound for \m{Q} function
\Disp{
\NC Q(x)
\leq \NC \F{1}{2} \RM{e}^{-x^2/2} \NR
}
Particularly, for \m{x =\R{2 \log N_g}}, according to CLT,
\Disp{
\NC Q(\R{2 \log N_g})
=\NC \F{1}{N_g}. \NR
}

@@

\Result
{Lemma}
{
Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in ().
%
\Disp{
\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
\leq \NC  4 \R{\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
}

To show this, by definition
%
\Disp{
\NC \IP{ \V{z} -(\V{y} -\M{P} \hat{\V{g}}), \M{P} (:,n_y) }
= \NC \IP{ \M{P} \hat{\V{g}} -\M{P} \V{g}, \M{P} (:,n_y) } \NR
\NC = \NC \IP{ \M{P} \V{d}, \M{P} (:,n_y) } \NR
}

By construction
\Disp{
\NC \VNm { \M{P} (:,n_y)^\H (\V{y} -\M{P} \hat{\V{g}}) } 
\leq \NC \VNm { \M{P}^\H (\V{y} -\M{P} \hat{\V{g}}) } _\infty \NR
\NC \leq \NC 2\R{\log N_g} \NR
}
By triangle inequality, together with Lemma (), we have
\Disp{
\NC \VNm {\M{P} (:,n_y)^\H \M{P} \V{d}} 
\leq \NC \VNm {\IP{ \V{z}, \M{P} (:,n_y) }}  +\IP{ \V{y} -\M{P} \hat{\V{g}}, \M{P} (:,n_y) } \NR
\NC \leq \NC 2 \R{\log N_g} +2 \R{\log N_g} \NR
}
which implies
\Disp{
\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
\leq \NC 4 \R{\log N_g}. \NR
}

@@

\Result
{Lemma}
{
Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in () with respect to \m{\d_s}.
%
\Disp{
\NC \VNm {\V{d}_{\MC{AB}}} _2
\leq \NC \F{1}{1-\d_{2s}} \VNm {P_{\MC{A}\MC{B}}^\Tr P d} _2 +\F{\d_{3s}}{(1-\d_{2s}) \R{s}} \VNm {d_{C}} _1 \NR
}
%
}

@@

\Result
{Lemma}
{
Let \m{\V{d}} be defined as above.
Then
%
\Disp{
\NC \VNm {\V{d}} _2^2
\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{s} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
}
%
}

@@

We can now formulate and prove the main bound of ours.
Here, we use \m{s=L} as the sparsity threshold.

\Result
{Theorem}
{
Let \m{\V{y}}, \m{\M{P}}, \m{\V{g}}, \m{\hat{\V{g}}}, \m{\V{d}} be defined as above.
Then
\Disp{
\NC \VNm {\V{d}} _2
\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp{
\NC \VNm {\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}} _2
\leq \NC \VNm {\M{P}^\Tr \M{P} \V{d}} _2 \NR
\NC \leq \NC \R{N_g} \VNm {\M{P}^\Tr \M{P} \V{d}} _\infty \NR
\NC \leq \NC 4 \R{ N_g \log N_g } \NR
}
Thus, by virtue of Lemma (),
\Disp{
\NC \VNm { \V{d}_{A} } _1
\leq \NC \R{L} \VNm { \V{d}_{A} } _2 \NR
\NC \leq \NC \R{L} \VNm { \V{d}_{\MC{AB}} } _2 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
}

As the next step, we must eliminate \m{\VNm {d_{\MC{A}}} _1} in rhs of Lemma ().
\Disp{
\NC \VNm { \V{d}_{\MC{C}} } _1
\leq \NC \VNm { \V{d}_{\MC{A}} } _1 +2 \VNm { \V{g}_{\MC{C}} } _1 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1
+2 \VNm { \V{g}_{\MC{C}} } _1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
}
Or,
\Disp{
\NC \VNm { \V{d}_{\MC{C}} } _1
\leq \NC 2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V{g}_{\MC{C}} } _1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g} \NR
}

We are ready to bound \m{\VNm { d } _2^2}.
Using Lemma () again, we have
\Disp{
\NC \VNm { \V{d} } _2^2
\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{L} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
\NC \leq \NC  \RB{ \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} } \VNm {\V{d}_{\MC{C}}} _1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \VNm {\V{d}_{\MC{C}}} _1 \NR
\NC \NC \quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \NR
}
Finally, plug in the bound for \m{\VNm {\V{d}_{\MC{C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m{\VNm {\V{d}_{\MC{C}}} _1}.
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
\NC 1 \ll \NC L \NR
\NC \ll \NC N_g \NR
}
And expand to the first order expressions containing \m{\d_{2L}} or \m{\d_{3L}} in the denominator using
\Disp{
\NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
}
Then
\Disp{
\NC \VNm {\V{d}} _2^2
\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}

>>>>

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_g}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \m {\RM {supp} (\V {g})} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse

@@

We apply DS to find \m {\hat {\V {g}}}, setting
\Disp {
\NC \gamma = \NC \R {2 \log N_g} \NR[+]
}

Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp {
\NC \V {d} = \NC \hat {\V {g}} -\V {g} \NR[+]
}
%
And call
\startitemize
\item \m {\MC {A}} be the largest \m {s} position of \m {g}.
\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T(N_g) -\MC {A}}}.
\item \m {\MC {C} =T \RB {N_g} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
\stopitemize

Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
Let \m {S:\; \MB {V}_{\MB {K}} (N) \mapsto \MB {V}_{\MB {K}} (N)}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} (N))}, so that
\Disp {
\NC \Nm {S \RB {x} \DB {n_1}} \geq  \NC \Nm {S \RB {x} \DB {n_2}}, \NR[+]
\NC n_1 > \NC n_2,
\quad n_1, n_2 \in T\RB {N} \NR
}
Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m {S} throughout this article.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.

\Result
{Definition}
{
Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
For \m {x \in \MB {V}_{\MB {K}} (N)}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
\Disp {
\NC \Nm {S(x) \DB {n} } < \NC f (n),
\quad n \in T\RB {N}. \NR
}
}

\Result
{Definition}
{
For \m {\V {x} \in \MB {V}_{\MB {K}} (N)}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
\Disp {
\NC \sum_{n=s+1}^N \Nm {S(\V {x}) (n)}
\leq \NC R. \NR
}
}

\Result
{Lemma (Tentative)}
{
Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
Let \m {\f} be given, and array response \m {\V {a} (\f)} defined as in ().
Then \m {\V {a} (\f)} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
%
\Disp {
\NC R
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}
}

We show the lemma, which is the key to bounding the sparsity of \m {h}.
Recall the identity for Dirichlet kernel
%
\Disp {
\NC D (\f')
:= \NC \Nm { \sum_{n=0}^{N_H-1} \RM {e}^{i n \f'} } \NR
\NC = \NC \F {\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp {
\NC \sin x = \NC x -\F {x^3}{6} + \MC {O} (x^5), \quad x \ll 1 \NR
}
%
Actually it can be shown that we have a inequality
%
\Disp {
\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}, \NR[+]
\NC -\pi \leq \NC x \leq \pi \NR
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp {
\NC \Nm {D (\f') }
= \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
\quad 0 \leq \f' \leq \pi. \NR
}

Particularly, for arbitrary \m {\f}, find \m {k} so that
\Disp {
\NC \eta := \NC \f -\F {2\pi k}{N_H}, \NR[+]
\NC \Nm {\eta}
\leq \NC \F {2\pi}{N_H}. \NR
}
%
Then observe
\Disp {
\NC \RB {\M {K}^\H \V {a} (\f)} \DB {k}
=\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
}
So we need only bound
\Disp {
\NC R(\eta)
:=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
}
By the approximation of rectangle to integral,
\Disp {
\NC R(\eta) -\F {2\pi} {N_H}
\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
}
Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
\Disp {
\NC R(\f)
\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{(24 -\f'^2) \f'} d \f'
+\F {2\pi} {N_H} \NR
\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
-\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
+\F {2\pi} {N_H}
}
Notice the argument of log in the second term \m {<1}, and we drop that.
Also drop \m {2\pi /N_H} since it is small.
Furthermore the \m {2\pi} factor in log can be dropped too.
\Disp {
\NC R(\f)
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}

\Result
{Lemma (Tentative)}
{
Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)}, and linear array response \m {\V {a}} defined as in ().
Let \m {\V {g}} be defined as above.
Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
%
\Disp {
\NC R
\leq \NC \F {L}{\pi^2} \RB { \log \F {N_H}{L} }^2 \NR
}
}

@@

\Result
{Definition}
{
For \m {\MC {T}, \MC {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
%
\Disp {
\NC \Nm {\IP {P_{\MC {T}} h, P_{\MC {T}'} h'}}
\leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
}
}

@@

\Result
{Lemma}
{
Let \m {P} be given.
Then \m {\tau_{s, s'}} is bounded in both direction as follows,
\Disp {
\NC \d_{s+s'} -\max (\{\d_s, \d_{s'} \})
\leq \NC \tau_{s, s'} \NR
\NC \leq \NC \d_{s+s'}
}
}

Thus \m {\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \m {\d_s} only.

\Result
{Lemma}
{
Let \m {P} be i.i.d.\ Radmacher, as defined in Lemma ().
Then \m {P} is RIP according to \m {\d} for at least probability
\Disp {
\NC 1 -2 \RB { \F {12}{\d} }^s \exp \left[ - \RB { \F {\epsilon^2}{4} -\F {\epsilon^3}{6} } \F {\d}{2} N_p \right] \NR
}
}

@@

\Result
{Proposition}
{
Let \m {\V {g}} and \m {\V {d}} be defined as above.
Then
%
\Disp {
\NC \VNm {\V {d}_{\MC {C}}} _1
\leq \NC \VNm {\V {d}_{\MC {A}}} _1 +2\VNm {\V {g}_{\MC {C}}} _1 \NR
}
}

To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}},
\Disp {
\NC \VNm {\V {g}} _1
-\VNm {\V {d}_{\MC {A}}} _1
+\VNm {\V {d}_{\MC {C}}} _1
-\VNm {\V {g}_{\MC {C}}} _1
\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
}
In the first line, we recall \m {\V {g} =\V {g}_{\MC {A}}}.
On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
\Disp {
\NC \VNm {\V {g} +\V {d}} _1
=\NC \VNm {\hat {\V {g}}} _1 \NR
\NC \leq \NC \VNm {\V {g}} _1 \NR
}
The result follows by combining.

\Result
{Lemma}
{
Let \m {\V {z}} and \m {\M {P}} be defined as above.
Then
%
\Disp {
\NC \Nm {\IP { \V {z}, \M {P} (:, n_g) }}
\leq \NC  2 \R {\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
%
with overwhelming probability.
}

This only depends on the fact that \m {\M {P} (:, n_g)} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.

Recall the following bound for \m {Q} function
\Disp {
\NC Q(x)
\leq \NC \F {1}{2} \RM {e}^{-x^2/2} \NR
}
Particularly, for \m {x =\R {2 \log N_g}}, according to CLT,
\Disp {
\NC Q(\R {2 \log N_g})
=\NC \F {1}{N_g}. \NR
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
%
\Disp {
\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
}

To show this, by definition
%
\Disp {
\NC \IP { \V {z} -(\V {y} -\M {P} \hat {\V {g}}), \M {P} (:,n_y) }
= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} (:,n_y) } \NR
\NC = \NC \IP { \M {P} \V {d}, \M {P} (:,n_y) } \NR
}

By construction
\Disp {
\NC \VNm { \M {P} (:,n_y)^\H (\V {y} -\M {P} \hat {\V {g}}) } 
\leq \NC \VNm { \M {P}^\H (\V {y} -\M {P} \hat {\V {g}}) } _\infty \NR
\NC \leq \NC 2\R {\log N_g} \NR
}
By triangle inequality, together with Lemma (), we have
\Disp {
\NC \VNm {\M {P} (:,n_y)^\H \M {P} \V {d}} 
\leq \NC \VNm {\IP { \V {z}, \M {P} (:,n_y) }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} (:,n_y) } \NR
\NC \leq \NC 2 \R {\log N_g} +2 \R {\log N_g} \NR
}
which implies
\Disp {
\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
\leq \NC 4 \R {\log N_g}. \NR
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
%
\Disp {
\NC \VNm {\V {d}_{\MC {AB}}} _2
\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{(1-\d_{2s}) \R {s}} \VNm {d_{C}} _1 \NR
}
%
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} be defined as above.
Then
%
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
}
%
}

@@

We can now formulate and prove the main bound of ours.
Here, we use \m {s=L} as the sparsity threshold.

\Result
{Theorem}
{
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then
\Disp {
\NC \VNm {\V {d}} _2
\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp {
\NC \VNm {\M {P}_{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
\NC \leq \NC \R {N_g} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
\NC \leq \NC 4 \R {N_g \log N_g} \NR
}
Thus, by virtue of Lemma (),
\Disp {
\NC \VNm { \V {d}_{A} } _1
\leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
\NC \leq \NC \R {L} \VNm { \V {d}_{\MC {AB}} } _2 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
}

As the next step, we must eliminate \m {\VNm {d_{\MC {A}}} _1} in rhs of Lemma ().
\Disp {
\NC \VNm { \V {d}_{\MC {C}} } _1
\leq \NC \VNm { \V {d}_{\MC {A}} } _1 +2 \VNm { \V {g}_{\MC {C}} } _1 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1
+2 \VNm { \V {g}_{\MC {C}} } _1
+\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
}
Or,
\Disp {
\NC \VNm { \V {d}_{\MC {C}} } _1
\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\MC {C}} } _1
+\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_g \log N_g} \NR
}

We are ready to bound \m {\VNm {d} _2^2}.
Using Lemma () again, we have
\Disp {
\NC \VNm { \V {d} } _2^2
\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
+\F {8 \d_{3L}} {L (1-\d_{2L})^2} \R {N_g \log N_g} \VNm {\V {d}_{\MC {C}}} _1 \NR
\NC \NC \quad +\F {16}{(1-\d_{2L})^2} N_g \log N_g \NR
}
Finally, plug in the bound for \m {\VNm {\V {d}_{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\MC {C}}} _1}.
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp {
\NC 1 \ll \NC L \NR
\NC \ll \NC N_g \NR
}
And expand to the first order expressions containing \m {\d_{2L}} or \m {\d_{3L}} in the denominator using
\Disp {
\NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
}
Then
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}
